---
output:
  md_document:
    variant: markdown_github
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figure/",
  fig.height = 1
)
```

# Animated Palettes

Recycled code from [Karthik Ram's `wesanderson` palette](https://github.com/karthik/wesanderson)
with inspiration from [DL Miller's `beyonce` palette](https://github.com/dill/beyonce)


**Note**: Where as previously mentioned paletts used a different method for generating themed color palettes. I have opted for a different approach. I brief I used movie barcodes (in which every frame of a movie is shrunk to a couple pixel wide line), I then took the top 10 (using a k-means algorithm [palette generator](https://palettegenerator.com/)) most represented colors. 

Using this approach I have generated color palettes that represent the most dominant colors of a given movie. 

However, I am not sure I like the results all that much, I am working on implementing a better method for generating color palettes that better refects the artisticly dominant colors of a movie. So please check back at some point.

## Installation

```r
devtools::install_github("Eomesodermin/animated", force = TRUE)
```

## Usage

```{r, palettes_dummy}
library("animated")

# See all palettes
names(animated_palettes)
for(i in 1:length(animated_palettes)){
  print(animated(paste0(names(animated_palettes[i]))))
}
```

## Palettes

### A_Bugs_life

```{r, A_Bugs_life}
animated("A_Bugs_life")
```


### Aladdin

```{r, Aladdin}
animated("Aladdin")
```


### Finding_Nemo

```{r, Finding_Nemo}
animated("Finding_Nemo")
```

### Inside_out

```{r, Inside_out}
animated("Inside_out")
```

### Lion_King

```{r, Lion_King}
animated("Lion_King")
```

### Monsters_Inc

```{r, Monsters_Inc}
animated("Monsters_Inc")
```

### Ratatouille

```{r, Ratatouille}
animated("Ratatouille")
```

### Up

```{r, Up}
animated("Up")
```

