---
output:
  md_document:
    variant: markdown_github
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figure/",
  fig.height = 1
)
```

# Animated Palettes

Recycled code from [Karthik Ram's `wesanderson` palette](https://github.com/karthik/wesanderson)
with inspiration from [DL Miller's `beyonce` palette](https://github.com/dill/beyonce)


**Note**: Where as previously mentioned paletts used a different method for generating themed color palettes. I have opted for a different approach. I brief I used movie barcodes (in which every frame of a movie is shrunk to a couple pixel wide line), I then took the top 10 (using a k-means algorithm [palette generator](https://palettegenerator.com/)) most represented colors. 

Using this approach I have generated color palettes that represent the most dominant colors of a given movie. 

However, I am not sure I like the results all that much, I am working on implementing a better method for generating color palettes that better refects the artisticly dominant colors of a movie. So please check back at some point.

## Installation

```r
devtools::install_github("Eomesodermin/animated", force = TRUE)
```

## Usage

```{r, Usage, eval=FALSE, echo=TRUE}
# Load library
library("animated")

# List of all palettes currently available can be found using
names(animated_palettes)

# To call a specific palette use 
animated("Aladdin")

# All current palettes are n = 10
# to interpolate more colors for a specific palette use 
animated("Aladdin", 21, type = "continuous")

```

## Palettes

```{r, all_palettes, echo=FALSE, eval = TRUE}
library("animated")

for(i in 1:length(animated_palettes)){
  print(animated(paste0(names(animated_palettes[i]))))
}

```

